---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# milRex

<!-- badges: start -->
[![R-CMD-check](https://github.com/datapumpernickel/milRex/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/datapumpernickel/milRex/actions/workflows/R-CMD-check.yaml)

[![codecov](https://codecov.io/gh/datapumpernickel/milRex/graph/badge.svg?token=08ULI3CEWH)](https://codecov.io/gh/datapumpernickel/milRex)


<!-- badges: end -->

The goal of milRex is to make it easy to query military expenditure data from 
SIPRI. 

# 🚧 Under construction 🚧

Currently this package is under construction. Only constant USD of military 
expenditure are queried. 

## Installation

You can install the development version of 
milRex from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("datapumpernickel/milRex")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = F}
library(milRex)
data <- mr_get_data()
```
