---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# milRex

<!-- badges: start -->
[![R-CMD-check](https://github.com/datapumpernickel/milRex/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/datapumpernickel/milRex/actions/workflows/R-CMD-check.yaml) [![codecov](https://codecov.io/gh/datapumpernickel/milRex/graph/badge.svg?token=08ULI3CEWH)](https://codecov.io/gh/datapumpernickel/milRex)


<!-- badges: end -->

The goal of milRex is to make it easy to query military expenditure data from 
SIPRI. 


expenditure are queried. 

## Installation

You can install the development version of 
milRex from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("datapumpernickel/milRex")
```

## Getting Military Expenditure in constant USD

This would query all the data, for military expenditure in constant USD. 

```{r example, eval = F}
library(milRex)
data <- mr_get_data(indicator = "constantUSD", 
                    cache = TRUE,
                    verbose = FALSE,
                    footnotes = FALSE)
```

The available indicators are: 

```{r labels, echo = F, message=F, warning=F}
library(dplyr)
library(knitr)
dplyr::tribble(
  ~sheet_name, ~unit,~skip,~indicator,
  "Constant (2022) US$", 2, 5,'constantUSD',
  "Current US$", 2, 5,'currentUSD',
  "Share of GDP", 1, 5,'shareOfGDP',
  "Share of Govt. spending", 3, 7,'shareGovt',
  "Regional totals", 2, 13,'regionalTotals',
  "Local currency financial years", 2, 7,'currencyFY',
  "Local currency calendar years", 2, 6,'currencyCY',
  "Per capita", 2, 6,'perCapita') |> 
  dplyr::select(sheet_name, indicator) |> 
  knitr::kable()
```



## Sources and Methods

Military Expenditure is a concept that is difficult to measure adequately in a 
comparative manner across the globe. The dataset by SIPRI is the best effort
that exists today, using only open sources. Nonetheless, there is limitation to
their data. I **highly** encourage anyone who wants to use this dataset, to read 
their Sources and Methods section here: 

https://www.sipri.org/databases/milex/sources-and-methods 

## Estimates and uncertain data

Some of the SIPRI estimates reported in their dataset are marked as uncertain 
or estimations (e.g. all the data for China). These cells are marked in blue or 
red in the resulting excel-file. Unfortunately, color coding is not 
machine-readable, hence this information cannot be translated into data.frames 
in R and is missing. Please be aware of this limitation. 

## Copyright

The Stockholm International Peace Research Institute limits the copying and 
redistribution of its data to the following two use-cases: 

* the excerption of SIPRI copyrighted material for such purposes as criticism, 
comment, news reporting, teaching, scholarship or research in which the use 
is for non-commercial purposes
* the reproduction of less than 10 per cent of a published data set. 

Hence, this package does **not** contain any SIPRI data itself. It merely 
automatizes the access through the website, by making the corresponding POST 
request and cleaning the resulting xlsx file into tidy formats.

Please make sure to cite SIPRI when using their data with: 

*SIPRI Military Expenditure Database 2024, https://www.sipri.org/databases/milex*
